### 2024-11-23 paper/background.tex
Minor change

% Structured Control Flow
\red{Wasm supports control instructions for structured control flow, which
eliminates the need for arbitrary jumps, ensuring structured and predictable
execution.
Control instructions include \texttt{blocks}, \texttt{call}, \texttt{br}, and
\texttt{return}, which are explicitly delimited in the code.
Each control instruction is associated with \textit{contexts} that facilitate
structured execution and support handling nested or complex control flows.
For instance, the \texttt{block} instruction groups a sequence of instructions
and provides a scoped execution context with a \textit{label}, while the
\texttt{call} instruction executes body of a function with a \textit{frame}.
The \texttt{br} and \texttt{return} instructions jump to the beginning or
the end of the block and the function, specified within the contexts.
}

>>>>

% Structured Control Flow
\red{Wasm supports control instructions for structured control flow, which
eliminates the need for arbitrary jumps, ensuring structured and predictable
execution.
Control instructions include \texttt{block}, \texttt{call}, \texttt{br}, and
\texttt{return}, which are explicitly delimited in the code.
Each control instruction is associated with \textit{contexts} in the stack that
facilitate structured execution and support handling nested or complex control
flows.
For instance, the \texttt{block} instruction groups a sequence of instructions
and provides a scoped execution with pusing a \textit{label} onto the stack,
while the \texttt{call} instruction executes the body of a function with
pushing a \textit{frame} onto the stack.
The \texttt{br} and \texttt{return} instructions jump to the beginning or
the end of the block and the function, specified in the contexts.
}
